\documentclass[12pt]{article}

\topmargin=-0.5in
\oddsidemargin=0in
\evensidemargin=0in
\textwidth=6.5in
\textheight=9.0in

\usepackage{color}
\usepackage{xspace}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{syntax}
\usepackage{url}
\usepackage{fancyhdr}
\usepackage{listings}

\input{defs}

\begin{document}
 \begin{large}
\begin{center}
Data Management Plan
\end{center}
\end{large}
\setcounter{page}{1}

\paragraph{Expected Data} The research conducted under this award will
create four kinds of data:

\begin{enumerate}
\item \textit{Platform Code:} The implementation of our platform for supporting \rasp development in Haskell.

\item \textit{Application Code:} The implementation of \rasp applications, such as \rasp-enabled Autobahn and clients of
\rasp-enabled Autobahn.

\item \textit{Data:} These data include the inputs that we use to evaluate our results.  These data also include the outputs from our research artifacts, including synthesized programs.

\item \textit{Metadata:} These data include the information needed to
  replicate all of our experiments, including installation instructions,
  command-line options, and experimental setup. 
\end{enumerate}

\paragraph{Period of data retention} Our results will be disseminated in
a timely fashion through publications and through periodic updates on
a project web page. The web page will be maintained at Github and will
provide code, evaluation data, and meta-data.  It will also contain information about the project's
vision and participants; access to papers documenting the fundamental
research results of this project; input data sets for evaluations;
explicit setup and results from experiments; documented potential uses
of our approaches and their applicability to other domains. 

The data will be made available immediately after
publication, and in some cases will be made available to reviewers
before publication. We will keep the data for at least three years
after the end of the project. We will host all of the data on Github. 
In the case where personnel on the grant will change affiliation
(because of graduation, separation, or other circumstances), the data
will be the responsibility of the PI and Co-PIs. 

\paragraph{Policies for access and sharing} 
Published data such as articles, dissertations and book chapters will
be accessible from publishers or on researcher web pages, subject to privacy, confidentiality, security, and
intellectual-property-right policies of individual publishers.

\end{document}
